Supplement to ``{\mytitle}''

### 2024-04-03 si/confidenceIntervals.Rnw
Added computation times to supplement, as requested by a reviewer

In this section we provide confidence intervals for all model parameters, excluding those that take unique values for each spatial unit.
For each model and parameter, we use principles of profile likelihood to obtain confidence intervals \cite{pawitan01}.
Due to the non-linear and stochastic nature of Models~1 and 3, exact evaluations of the profile log-likelihood are difficult to obtain.
Instead, the log-likelihood at each point of the profile is estimated using via Monte-Carlo based particle filter methods.
We therefore obtain confidence intervals for the parameters of Model~1 and Model~3 using the Monte Carlo adjust profile (MCAP) algorithm \cite{ionides17}.

In each subsection, we provide figures that show the curvature of the profile log-likelihood near the MLE (Figures~\ref{fig:m1Profs}--\ref{fig:m3Profs}). 
In these figures, the parameter values are shown on the transformed scale in which the profile was calculated.

@@

Parameter estimates for Model~1, along with the MCAP confidence intervals for the estimate, are given in Table~\ref{tab:mod1CI}. 
Figure~\ref{fig:m1Profs} displays the Monte Carlo evaluations of the profile likelihood values, obtained using a particle filter.

@@

Parameter estimates for Model~3, along with the MCAP confidence intervals for the estimate, are given in Table~\ref{tab:mod3CI}. 
Figure~\ref{fig:m3Profs} displays the Monte Carlo evaluations of the profile likelihood values, obtained using a particle filter.

>>>>

In this section we provide confidence intervals for all model parameters, excluding those that take unique values for each spatial unit.
For each model and parameter, we use principles of profile likelihood to obtain confidence intervals \citep{pawitan01}.
Due to the non-linear and stochastic nature of Models~1 and 3, exact evaluations of the profile log-likelihood are difficult to obtain.
Instead, the log-likelihood at each point of the profile is estimated using via Monte-Carlo based particle filter methods.
We therefore obtain confidence intervals for the parameters of Model~1 and Model~3 using the Monte Carlo adjust profile (MCAP) algorithm \citep{ionides17}.

Profile confidence intervals for nonlinear POMP models are require a large number of computations. In the Model~1 and Model~3 subsections, we mention the total computational expense of each profile log-likelihood evaluation. Each subsection also provide figures that show the curvature of the profile log-likelihood near the MLE (Figures~\ref{fig:m1Profs}--\ref{fig:m3Profs}).
In these figures, the parameter values are shown on the transformed scale in which the profile was calculated.

@@

Parameter estimates for Model~1, along with the MCAP confidence intervals for the estimate, are given in Table~\ref{tab:mod1CI}.
Figure~\ref{fig:m1Profs} displays the Monte Carlo evaluations of the profile likelihood values, obtained using a particle filter.
The total computational burden of this profile likelihood search was 3631 hours, which was computed in parallel using 9675 separate jobs via the \texttt{batchtools} R package \citep{batchtools}.

@@

Parameter estimates for Model~3, along with the MCAP confidence intervals for the estimate, are given in Table~\ref{tab:mod3CI}.
Figure~\ref{fig:m3Profs} displays the Monte Carlo evaluations of the profile likelihood values, obtained using a particle filter.
The total computational burden of this profile likelihood search was 28938 hours, which was computed in parallel using 7568 separate jobs via the \texttt{batchtools} R package \citep{batchtools}.
